### 2025-07-09 README.Rmd
update readme

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/master?urlpath=rstudio) [![DOI:10.17605/OSF.IO/J58K](https://img.shields.io/badge/DOI-10.17605/OSF.IO/J58KH-brightgreen.svg)](http://doi.org/10.17605/OSF.IO/J58KH)

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `renv::install()` to ensure you have the packages this analysis depends on 
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/main?urlpath=rstudio) [![DOI:10.17605/OSF.IO/J58K](https://img.shields.io/badge/DOI-10.17605/OSF.IO/J58KH-brightgreen.svg)](http://doi.org/10.17605/OSF.IO/J58KH)

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `renv::restore()` to ensure you have the packages this analysis depends on 
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console
